Journal Article Summaries

### 2025-04-01 docs/logbook.tex
Worked on mesh pipeline and read papers
updated logbook

>>>>

	\begin{MeetingMinutes}{Fri 14/3/2025}{u7013004}
		Possibly learn the offsets so I can use offset\_verts but that requires a packed tensor I believe. Might as well just start a new set of vertices I reckon.
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Sun 30/3/2025}{u7013004}
		The edge loss didn't work on Friday. Let's think about why.

		If X is the result after Chamfer loss backwards, then it won't conform to the volume constraints. If Y is the malleable mesh, then decreasing SSE between Y and X will decrease the error in positions of Y and X subjecting Y to have constant volume. Preserving the edge length constraint can result in Y being as close to X. As a result, the solver might just choose to focus on minimising SSE and edge length constraints could assist in that.

		Okay, the issue is that if I do Edge loss by itself, the gradient blows up. Why? Because the Hessian (double derivative of objective with respect to Y twice) is apparently incredibly ill-conditioned. ChatGPT says it's because of

		2.1 Edge Lengths Close to Their Targets (Small Gradients): if $d(Y_i, Y_j)^2 \approx d(X_i, X_j)^2$ then the scaling term $d(Y_i, Y_j)^2 - d(X_i, X_j)^2$ is small. This means the Hessian matrix has many small entries, leading to near-zero eigenvalues and an ill-conditioned system.

		2.2 Highly Connected Meshes (Near-Dependent Constraints): If a vertex has many connected neighbors, its position is constrained by multiple edges. This causes rows of the Hessian to be nearly linearly dependent, leading to a large condition number.

		2.3 The Rigid Motion Null Space: The edge length term does not penalize rigid transformations, meaning there are six zero eigenvalues (three for translation, three for rotation), making 
		$f_{YY}$ singular
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Tue 1/4/2025}{u7013004}
		Wtf it's the 1st of April. After the past four days, I've found that the edge length constraint is kinda bad and not worth spending more time on. 
		The next phase is to keep writing my thesis, and to write scripts for average performance, and also test a little bit of robustness with edges today. I can plan out my day.

		For my thesis, I would like to plan out my roadmap and write my abstract. My dad would like me to write a problem definition, idk if I'll use it but I'll do it to make him happy. 
	\end{MeetingMinutes}
